Evaluating `Graphical Perception' with CNNs

### 2018-03-30 PAPER/paper.tex
Switch paper title and start new experiments.
Update paper and figures.
bib ref change; squash

\usepackage{microtype}                 % use micro-typography (slightly more compact, better to read)
\PassOptionsToPackage{warn}{textcomp}  % to address font issues with \textrightarrow
\usepackage{textcomp}                  % use better special symbols
\usepackage{mathptmx}                  % use matching math font
\usepackage{times}                     % we use Times as the main font
\renewcommand*\ttdefault{txtt}         % a nicer typewriter font
\usepackage{cite}                      % needed to automatically sort the references
\usepackage{tabu}                      % only used for the table example
\usepackage{booktabs}                  % only used for the table example
\usepackage{makecell}
\usepackage{multirow}

@@

%% Paper title.
% James' title suggestions
% - Reproducing 'Graphical Perception' with CNNs
% - 
\title{Reproducing 'Graphical Perception' with CNNs}

@@

%% indicate IEEE Member or Student Member in form indicated below
%\author{Daniel Haehn, \textit{Member, IEEE}, James Tompkin, and Hanspeter Pfister}
\author{Daniel Haehn, James Tompkin, and Hanspeter Pfister}
\authorfooter{
%% insert punctuation at end of each item
\item Daniel Haehn, and Hanspeter Pfister are with the Paulson School of Engineering and Applied Sciences at Harvard University. \\
E-mail: \{haehn,pfister\}@seas.harvard.edu.
%
\item James Tompkin is with the Thomas J. Watson Sr. Center for Information Technology at Brown University. \\E-mail: james\_tompkin@brown.edu.
}

%other entries to be set up for journal
\shortauthortitle{Haehn \MakeLowercase{\textit{et al.}}: Computing Graphical Perception with Convolutional Neural Networks}
%\shortauthortitle{Firstauthor \MakeLowercase{\textit{et al.}}: Paper Title}

@@

\bibliography{paper.bib}
\end{document}

>>>>

\usepackage{microtype}                 % use micro-typography (slightly more compact, better to read)
\PassOptionsToPackage{warn}{textcomp}  % to address font issues with \textrightarrow
\usepackage{textcomp}                  % use better special symbols
\usepackage{mathptmx}                  % use matching math font
\usepackage{times}                     % we use Times as the main font
\renewcommand*\ttdefault{txtt}         % a nicer typewriter font
\usepackage{cite}                      % needed to automatically sort the references
\usepackage{tabu}                      % only used for the table example
\usepackage{booktabs}                  % only used for the table example
\usepackage{makecell}
\usepackage{multirow}
\usepackage[export]{adjustbox}
\usepackage{subfig}

@@

%% Paper title.
% James' title suggestions
% - Reproducing 'Graphical Perception' with CNNs
% - 
\title{Evaluating `Graphical Perception' with CNNs}

@@

%% indicate IEEE Member or Student Member in form indicated below
%\author{Daniel Haehn, \textit{Member, IEEE}, James Tompkin, and Hanspeter Pfister}
\author{Daniel Haehn, James Tompkin, and Hanspeter Pfister}
\authorfooter{
%% insert punctuation at end of each item
\item Daniel Haehn, and Hanspeter Pfister are with the Paulson School of Engineering and Applied Sciences at Harvard University. \\
E-mail: \{haehn,pfister\}@seas.harvard.edu.
%
\item James Tompkin is with Brown University. \\E-mail: james\_tompkin@brown.edu.
}

%other entries to be set up for journal
\shortauthortitle{Haehn \MakeLowercase{\textit{et al.}}: Evaluating `Graphical Perception' with CNNs}
%\shortauthortitle{Firstauthor \MakeLowercase{\textit{et al.}}: Paper Title}

@@

\bibliography{paper}
\end{document}
